\section{\sc Publications}

%{Alekseenko, A.; McKinlay, C.; Shapiro, B.; Shubin, C.; \emph{Participation Metrics in Online Tutoring}. Journal of Online Learning and Teaching, In Review.}

{McKinlay, C.; Knights, D.;  Vangay, P.; Knight, R.; \emph{Differential Abundance Tests for Microbiome Data}. Nature Methods, In Review.}

{Knights, D.; Ward, T.; McKinlay, C; Miller, H.; Gonzalez, A.; McDonald, D.; Knight, R.; \emph{Rethinking “Enterotypes”}. Cell Host and Microbe, Vol. 16, 10/14.}

{Knights, D.; Huang, H; Vangay, P.: McKinlay, C.; \emph{Multi-omics Analysis of Inflammatory Bowel Diseases}. Immunology Letters, Vol. 10, 08/14}

{McKinlay, C.; \emph{Hacking OkCupid: Optimizing Visibility in a Bipartite Social Network}. Computer-Supported Cooperative Work and Social Computing, Vol. 16, 02/13}

{Lord, J.; Rast, M.; McKinlay, C.; Clyne, J.; Mininni, P.; \emph{Wavelet Decomposition of Forced Turbulence: Applicability of the Iterative Donoho-Johnstone Threshold}. Physics of Fluids Vol. 24, 02/12.}

{Lord, J.; Rast, M.; McKinlay, C.; Clyne, J.; Mininni, P.; \emph{Wavelet Decomposition of Taylor-Green Forced Turbulence: Sensitivity of the incoherent Component Statistics to Threshold Value}. American Geophysical Union, 09/10.}

{McKinlay, C.; Citro, C.; \emph{Scalable Application of Compressed Linear Operators on GPU Hardware}. 14th SIAM Conference on Parallel Processing for Scientific Computing, 01/10.}

{McKinlay, C.; \emph{Efficient Algebraic Representations for Throughput-Oriented Algorithms}. Doctoral Dissertation, 06/13 }

%{Mckinlay, C.; Citro, C.; \emph{Efficient Multi-precision Arithmetic with GPUs}. In preparation.}
